Online {\IterComp}

### 2017-09-14 work.tex
fix intro; add figure about work-efficiency 'motivation'.

@@

>>>>

\begin{figure}[t]
    \centering
    \includegraphics[width=0.5\textwidth]{figs/motivation-work-efficiency.pdf}
    \caption{Relationship between work efficiency vs speedup for 500 different binaries of \texttt{susan\_c}.
            Each point represents averages over a subset of all inputs.}
    \label{fig:motivation-work-efficiency}
\end{figure}

\FIXME{Rodrigo: I think we could show how the work efficiency metric performs compared with speedup, the same way we showed the other metrics does not work well.}

@@

\FIXME{Rodrigo: Perhaps we could remove this section, since we have already discussed the IPC in the Motivation.}
